Plots and tables summarizing results of Poisson simulations

### 2018-12-20 analysis/poisson.Rmd

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
	  theme(axis.line = element_blank())
p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
	  scale_x_discrete(breaks = NULL) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
	  theme(axis.line = element_blank())
p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
	  scale_x_discrete(breaks = NULL) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
	  theme(axis.line = element_blank())
plot_grid(p1,p8,p128,nrow = 1,ncol = 3)
```

@@

```{r angles-violin-plots, fig.height=3.5, fig.width=10}
mise.hf.ti.r.ang.1   <- colMeans(rbind(mise.hf.ti.r.4.ang.1,
                                       mise.hf.ti.r.5.ang.1,
                                       mise.hf.ti.r.6.ang.1,
					  				   mise.hf.ti.r.7.ang.1))
mise.hf.ti.r.ang.8   <- colMeans(rbind(mise.hf.ti.r.4.ang.8,
 									   mise.hf.ti.r.5.ang.8,
                                       mise.hf.ti.r.6.ang.8,
                                       mise.hf.ti.r.7.ang.8))
mise.hf.ti.r.ang.128 <- colMeans(rbind(mise.hf.ti.r.4.ang.128,
                                       mise.hf.ti.r.5.ang.128,
                                       mise.hf.ti.r.6.ang.128,
									   mise.hf.ti.r.7.ang.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.1,mise.BMSM.ang.1,mise.ash.ang.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.8,mise.BMSM.ang.8,mise.ash.ang.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.ang.128,mise.BMSM.ang.128,mise.ash.ang.128))
p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
	  theme(axis.line = element_blank())
p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
	  scale_x_discrete(breaks = NULL) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
	  theme(axis.line = element_blank())
p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
	  scale_x_discrete(breaks = NULL) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
	  theme(axis.line = element_blank())
plot_grid(p1,p8,p128,nrow = 1,ncol = 3)
```

@@

>>>>

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
create.violin.plots <- function (pdat1, pdat8, pdat128) {
  p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
	    theme(axis.line = element_blank())
  p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
  	    scale_x_discrete(breaks = NULL) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
	    theme(axis.line = element_blank())
  p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
 	    scale_x_discrete(breaks = NULL) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
	    theme(axis.line = element_blank())
  return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))
}
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r angles-violin-plots, fig.height=3.5, fig.width=10}
mise.hf.ti.r.ang.1   <- colMeans(rbind(mise.hf.ti.r.4.ang.1,
                                       mise.hf.ti.r.5.ang.1,
                                       mise.hf.ti.r.6.ang.1,
					  				   mise.hf.ti.r.7.ang.1))
mise.hf.ti.r.ang.8   <- colMeans(rbind(mise.hf.ti.r.4.ang.8,
 									   mise.hf.ti.r.5.ang.8,
                                       mise.hf.ti.r.6.ang.8,
                                       mise.hf.ti.r.7.ang.8))
mise.hf.ti.r.ang.128 <- colMeans(rbind(mise.hf.ti.r.4.ang.128,
                                       mise.hf.ti.r.5.ang.128,
                                       mise.hf.ti.r.6.ang.128,
									   mise.hf.ti.r.7.ang.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.1,mise.BMSM.ang.1,mise.ash.ang.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.8,mise.BMSM.ang.8,mise.ash.ang.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.ang.128,mise.BMSM.ang.128,mise.ash.ang.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r heavisine-table, results="asis"}
mise.ang.table   <- cbind(mise.hs.1[methods],
                          mise.hs.8[methods],
                          mise.hs.128[methods])
rownames(mise.hs.table) <- table.row.names
colnames(mise.hs.table) <- table.col.names
print(xtable(mise.hs.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```
